---
title: " Long Project title"
author: "Name"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2: 
    toc: TRUE
    toc_float: TRUE
    number_sections: true
    self_contained: yes
    css: hmri-style.css
    code_folding: hide  
    

---

<script>
  $(document).ready(function() {
    $('#TOC').parent().prepend('<div id=\"nav_logo\"><img src=\"hmri.png"></div>');
  });
</script>

<style>
#nav_logo {
  width: 90%;
  margin-top: 20px;
}
</style>


<div class="watermark">DRAFT</div>




```{r, include = FALSE}

library(tidyverse)
library(here)
library(kableExtra)
require(Hmisc)
knitrSet(lang='markdown', h=4.5, fig.path='png/', fig.align='left',
         capfile='captions.md')  # + sometimes ,cache=TRUE
# knitrSet redirects all messages to messages.txt
options(grType='plotly') # for certain graphics functions
mu <- markupSpecs$html   # markupSpecs is in Hmisc
cap  <- mu$cap           # function to output html caption
lcap <- mu$lcap          # for continuation for long caption
# These last 2 functions are used by the putHfig function in Hmisc
cat('', file='captions.md')   # initialize table of short captions

```




# Introduction



## Using the Hmisc library


The Hmisc library has several useful fuinctions for reading and anotating
datasets, including labels and units. There is also a useful html integration
for some of hte commands. 

In the below code, the upData command is used to create a new variable as well
as labels and units. A data dictionary printout is also given in html format
wiht the html and contents commands.

```{r metadata,results='asis'}
getHdata(pbc)

# Have upData move units from labels to separate attribute
pbc <- upData(pbc,
              fu.yrs = fu.days / 365.25,
              labels = c(fu.yrs = 'Follow-up Time',
                         status = 'Death or Liver Transplantation'),
              units = c(fu.yrs = 'year'),
              drop  = 'fu.days',
              moveUnits=TRUE, html=TRUE)
# The following can also be done by running this command
# to put the results in a new browser tab:
# getHdata(pbc, 'contents')
html(contents(pbc), maxlevels=10, levelType='table')
```

There are also useful descriptive statistics functions, for unstratified, and
stratified summaries of the data. The describe and summaryM functions have great
tabular reporting outputs, as well as informative plots. Some examples below


```{r describe,results='asis'}
# did have results='asis' above
d <- describe(pbc)
html(d, size=80, scroll=TRUE)

# prList is in Hmisc; useful for plotting or printing a list of objects
# Can just use plot(d) if don't care about the mess
# If using html output these 2 images would not be rendered no matter what
p <- plot(d)
# The option htmlfig=2 causes markupSpecs$html$cap() to be used to
# HTML-typeset as a figure caption and to put the sub-sub section
# marker ### in front of the caption.  htmlfig is the only reason
# results='asis' was needed in the chunk header
# We define a long caption for one of the plots, which does not appear
# in the table of contents
# prList works for html notebooks but not html documents
# prList(p, lcap=c('', 'These are spike histograms'), htmlfig=2)
```


```{r plotlym,cap='This used the <code>htmltools tagList</code> function.',scap='Two <code>plotly</code> graphics combined into one'}
htmltools::tagList(p)    # lapply(p, plotly::as.widget)
```



```{r summaryM,cap=paste('Proportions and', mu$chisq(), 'tests for categorical variables')}
s <- summaryM(bili + albumin + stage + protime + sex + age + spiders +
              alk.phos + sgot + chol ~ drug, data=pbc,
							overall=FALSE, test=TRUE)
plot(s, which='categorical')
```


```{r summaryM2,results='asis',cap='Extended box plots for the first 4 continuous variables'}
plot(s, which='continuous', vars=1 : 4)
```

```{r summaryM3,cap='Extended box plots for the remaining continuous variables'}
plot(s, which='continuous', vars=5 : 7)

```

```{r summaryM4}
html(s, caption='Baseline characteristics by randomized treatment',
     exclude1=TRUE, npct='both', digits=3, middle.bold=TRUE,
     prmsd=TRUE, brmsd=TRUE, msdsize=mu$smaller2)
```
# Statistical analysis methods


# Results


## Using the rms library for regression models

```{r}
require(rms)
getHdata(lead)
# Subset variables just so contents() and describe() output is short
# Override units of measurement to make them legal R expressions
lead <- upData(lead,
               keep=c('ld72', 'ld73', 'age', 'maxfwt'),
               labels=c(age='Age'),
               units=c(age='years', ld72='mg/100*ml', ld73='mg/100*ml'))


```


To use Predict, summary, or nomogram in the rms package, you need to let rms first compute summaries of the distributional characteristics of the predictors

```{r}
dd <- datadist(lead); options(datadist='dd')
dd    # show what datadist computed
```


Fit an ordinary least squares regrssion model

```{r}
# Fit an ordinary linear regression model with 3 predictors assumed linear
f <- ols(maxfwt ~ age + ld72 + ld73, data=lead)

f$coef
```


Unfortunately, as far as I can tell there is no nice way to display the
regression table in HTML. This could be done manually


beta = coef(olsfit).
se =  sqrt(diag(vcov(olsfit)))
p = 1 - pchisq(Z^2, 1)  

To get t-statistic pvalues need to know the df ...
Z <- beta/se
p = 2 * (1 - pt(abs(Z), errordf))


Another approach is to use print.capture see https://stackoverflow.com/questions/47724189/extract-all-model-statistics-from-rms-fits


```{r}
#parser
get_model_stats = function(x) {
  cap = capture.output(print(x))

  #model stats
  stats = c()
  stats$R2.adj = str_match(cap, "R2 adj\\s+ (\\d\\.\\d+)") %>% na.omit() %>% .[, 2] %>% as.numeric()

  #coef stats lines
  coef_lines = cap[which(str_detect(cap, "Coef\\s+S\\.E\\.")):(length(cap) - 1)]

  #parse
  coef_lines_table = suppressWarnings(readr::read_table(coef_lines %>% stringr::str_c(collapse = "\n")))
  colnames(coef_lines_table)[1] = "Predictor"

  list(
    stats = stats,
    coefs = coef_lines_table
  )
}


get_model_stats(f)
```


Residual plots:

```{r}
r <- resid(f)
par(mfrow=c(2,2))   # 2x2 matrix of plots
plot(fitted(f), r); abline(h=0)  # yhat vs. r
with(lead, plot(age,  r));    abline(h=0)
with(lead, plot(ld73, r));    abline(h=0)
qqnorm(r)           # linearity indicates normality
qqline(as.numeric(r))
```




# Discussion



# Appendix

```{r, echo=FALSE}

pander::pander(sessionInfo(), compact = FALSE)

```



