---
title: "Data management report: CRE19282"
author: "Chris Oldmeadow"
date: "`r Sys.Date()`"

output: html_document

---



# About

The is report decribes the steps taken to import the data, perform some basic descriptive statistics,  data quality checks, and create an analysis data set.

## Notes

The data was supplied in excel format, with the second row indicating formats for categorical variables. I manually deleted this row and created a new data formats file. The last two rows from this file also contained totals and other summaries which were also deleted.

## Required libraries
```{r}
library(tidyverse) # comprehensive data manipulation
library(readxl) # for reading excel
library(skimr) # some quick data summaries
library(janitor) # for cleaning excel data
library(knitr) # turning markdown into html
library(here) # reproducable directories
```

# Import the data



```{r}
```









# Summaries of the data


# Notes from the data summaries

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

In summary:

</div>

Finally we save the smaller dataset for analysis and presentation of results in the report


```{r}

saveRDS(adat, here("Data", "analysis.Rds"))

```
