---
title: "Data management report: CRE19282"
author: "Chris Oldmeadow"
date: "`r Sys.Date()`"

output: html_document

---



# About

The is report decribes the steps taken to import the data, perform some basic descriptive statistics,  data quality checks, and create an analysis data set.

## Notes

The data was supplied in excel format, with the second row indicating formats for categorical variables. I manually deleted this row and created a new data formats file. The last two rows from this file also contained totals and other summaries which were also deleted.

## Required libraries
```{r}
library(tidyverse) # comprehensive data manipulation
library(readxl) # for reading excel
library(skimr) # some quick data summaries
library(janitor) # for cleaning excel data
library(knitr) # turning markdown into html
library(here) # reproducable directories
```

# Import the data



```{r}
dat <- read_excel(here("Data",
		       "Current Audit Data 16.03.20 - HMRI.01.20.xlsx"))
```




```{r labels}
adat <- dat %>%
	janitor::clean_names() %>%
	select(-notes)

adat  <-  adat %>%
	mutate(sex = factor(sex, levels = c(0, 1), labels = c("Male", "Female")),
	       diagnosis = factor(diagnosis, levels = c(0,1), labels = c("Liquid","Solid")),
	       initial_dx_or_relapse = factor(initial_dx_or_relapse, levels = c(0,1), labels =  c("initial","relapse")),
	       initial_or_replacement = factor(initial_or_replacement, levels = c(0,1), labels = c("initial","replacement")),
               chemo_prior_to_insertion = factor(chemo_prior_to_insertion, levels = c(0,1), labels = c("no","yes")),
               type_of_skin_prep_used_in_ot = factor(type_of_skin_prep_used_in_ot, levels = c(0,1,2,3,4,5), labels = c("Chlorhexidine","Chlorhexidine + Alcohol", "Betadine", "betadine + alcohol", "chlorhexidine + cetrimide", "not specified")),
	       ot_antibiotic_prophylaxis = factor(ot_antibiotic_prophylaxis, levels = c(0,1,2,3), labels = c("no", "yes", "on regular IVABs", "not recorded")),
               antibiotic_type = factor(antibiotic_type, levels  = c(0,1,2,3,4,5), labels = c("no antibiotics", "other", "cefazolin", "flucloxacillin", "tazocin", "flucloxacillin + gentamicin" )),
               venous_site = factor(venous_site, levels = c(1,2,3,4,5), labels = c("internal jugular", "other", "external jugular",  "Cephalic", "other")),
               laterality = factor(laterality, levels = c(1,2,3), labels =  c("left", "right", "not available")),
               type_of_line = factor(type_of_line, levels = c(0,2,3), labels = c("Port", "External tunnelled", "Other")),
	       fever_7_days_prior_to_insertion = factor(fever_7_days_prior_to_insertion, levels = c(0,1), labels = c("no","yes")),
	       antibiotics_7_days_prior_to_insertion = factor(antibiotics_7_days_prior_to_insertion, levels = c(0,1), labels = c("no","yes")),
               wash_pre_op = factor(wash_pre_op, levels = c(0,1,2), labels = c("no","yes","not recorded")), 
               positive_culture_in_first_90_days = factor(positive_culture_in_first_90_days, levels = c(0,1), labels = c("no", "yes"))) 



adat <- adat %>%
	mutate(skin_prep = fct_collapse(as.character(as.numeric(type_of_skin_prep_used_in_ot)), "Chlorhexadine solution" = c("0","1","4"), 
							"Betadine solution" = c("2","3"), 
							"Not specified" = c("5","6")),
	       wash_pre_op = fct_recode(wash_pre_op, NULL = "not recorded"),
	       laterality = fct_recode(laterality, NULL = "not available"),
	       skin_prep = fct_recode(skin_prep, NULL = "Not specified"),
	       ot_antibiotic_prophylaxis = fct_recode(ot_antibiotic_prophylaxis, NULL = "not recorded"),
	       surgeon = factor(surgeon),
	ln_plt_dx = log(plt_at_dx))
```


There are many variables in this data set, with a mixture of numeric, character and date types as well. There are quite a few variables that aren't of interest statistically so these will be dropped from analyses. The following section specifies the numeric and character variables that we will restrict attention to.


```{r selecting}

vtypes <- as.data.frame(sapply(adat, class))
contvars <-rownames(vtypes[vtypes[,1]=="numeric",])
catvars <-rownames(vtypes[vtypes[,1]=="factor",])

#dput(contvars)
 contvars <- c(  "age_at_insertion_years",
  "wcc_at_dx", "anc_at_dx", "plt_at_dx", "peripheral_blasts",
 "weight_kg_at_insertion", "height_m_at_insertion", "bmi", "inpatient_days_prior_to_insertion",
 "no_of_steroid_days_prior_to_insertion",  "no_day_from_dx_to_cvl_insertion",
 "wash_pre_op")



#dput(catvars)
 cvars_short <- c("sex", "diagnosis", "sub_classification_of_diagnosis", "initial_dx_or_relapse",
 "initial_or_replacement", "chemo_prior_to_insertion", "type_of_skin_prep_used_in_ot",
 "ot_antibiotic_prophylaxis", "antibiotic_type", "venous_site",
 "laterality", "type_of_line", "positive_culture_in_first_90_days"
 )


```

# Summaries of the data

We can see summary statistics of each of the variables of interest to try and identify any errors or unusual values.

```{r}
adat %>%
	select(one_of(c(cvars_short,contvars))) %>%
	skim()

```





```

# Notes from the data summaries

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

In summary:

- There are `r length(unique(adat$id))` unique patients from `r nrow(adat)` observations
- There are no completely duplicated rows in the data
- White cell count, ANC and platelettes are very skewed and should be checked for errors, and summarised using medians/interquartile ranges

</div>

Finally we save the smaller dataset for analysis and presentation of results in the report


```{r}

saveRDS(adat, here("Data", "analysis.Rds"))

```
